Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-14 paper.tex
Fix up first intro paragraph

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical in scale if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important nondimensional parameter is often the Reynolds number, which
quantifies the importance of inertial forces over viscous forces on the flow
physics. It should be noted that in general the geometric scale of a physical
model is not necessarily the same as its dynamical scale. As such, hereafter we
will use the word ``scale'' to refer to this dynamical scale rather than the
geometric scale.

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important nondimensional parameter is often the Reynolds number, which
quantifies the importance of inertial forces over viscous forces on the flow
physics:
\begin{equation}
    \frac{Ul}{\nu},
    \label{eq:Re}
\end{equation}
where $U$ and $l$ are characteristic velocity and length scales, respectively,
and $\nu$ is the fluid kinematic viscosity. In general the geometric scale of a
physical model is not necessarily the same as its dynamical scale. As such,
hereafter we will use the word ``scale'' to refer to this dynamical scale or
Reynolds number.
